### 2022-03-27 chapters/intro/intro.tex
modifs post-defense part III

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics of the whole Great Barrier Reef \citep{lambrechts2008multi}. \modif{The 2D version of SLIM solves the shallow water equations, which assume a constant water density and compute depth-averaged current velocities. This model is therefore well suited for shallow areas where the water-column is well mixed. Furthermore, assuming homogeneous vertical profiles reduces the computational cost and allows a finer spatial resolution of the model. In deeper areas however, 3D baroclinic models are required to capture the variations of density in the water column due to pressure, temperature and salinity. These differences in density cause baroclinic instabilities that generate mesoscale eddies. However, 3D baroclinic models are computationally more expensive, which prohibits the use of a reef-scale resolution on the whole Florida Reef Tract. As most reefs of the Florida are located in areas shallower than 30 meters [\textbf{INSERT FIGURE}], we coupled the 2D version of SLIM with GOM-HYCOM to indirectly capture the impact of baroclinic instabilities on the connectivity of the Florida Keys. Using this approach, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT, \ie~the exchanges of larvae between reefs. The results of the model used in this thesis were validated against observations and showed good agreement with tide gauge and ADCP measurements, as illustrated in appendix \ref{onset:appendice} and chapter \ref{chap:irma}}.

@@

\modif{\section{Modeling framework and assumptions}}

\modif{Wave-Current coupling. Radiation stress vs vector force}

\modif{Presentation of the epidemiological model ?}

\modif{Hypotheses of the model/study}\newline

>>>>

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics of the whole Great Barrier Reef \citep{lambrechts2008multi}. \modif{The 2D version of SLIM solves the shallow water equations, which assume a constant water density and compute depth-averaged current velocities. This model is therefore well suited for shallow areas where the water-column is well mixed. Furthermore, assuming homogeneous vertical profiles reduces the computational cost and allows a finer spatial resolution of the model. In deeper areas however, 3D baroclinic models are required to capture the variations of density in the water column due to pressure, temperature and salinity. These differences in density cause baroclinic instabilities that generate mesoscale eddies. However, 3D baroclinic models are computationally more expensive, which prohibits the use of a reef-scale resolution on the whole Florida Reef Tract. As most reefs of the Florida are located in areas shallower than 30 meters (Fig. \ref{intro:bathy}), we coupled the 2D version of SLIM with GOM-HYCOM to indirectly capture the impact of baroclinic instabilities on the connectivity of the Florida Keys. Using this approach, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT, \ie~the exchanges of larvae between reefs. The results of the model used in this thesis were validated against observations and showed good agreement with tide gauge and ADCP measurements, as illustrated in appendix \ref{onset:appendice} and chapter \ref{chap:irma}}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{chapters/intro/figures/bathymetry_figure.png}
	\caption{\modif{Bathymetry of the Florida Keys and the Dry Tortigas. The bathymetry of the model was built by combining three data sources: the General Bathymetric Chart of the Ocean (\href{https://www.gebco.net/}{GEBCO};15 arc-seconds resolution), The Coastal Relief Model (\citealp{noaa2001}; 3 arc-seconds resolution), and NOAA's bathymetric Digital Elevation Model (\citealp{ncei2018}; 1/3 arc-second resolution).}}
	\label{intro:bathy}
\end{figure}

@@

%\modif{\section{Modeling framework and assumptions}}

%\modif{Wave-Current coupling. Radiation stress vs vector force}

%\modif{Presentation of the epidemiological model ?}

%\modif{Hypotheses of the model/study}\newline
